\textit{MSF: Modulated Sub-graph Finder}

### 2018-07-31 MSF_Paper_FA.tex
add tag to Ivos comment

Existing pathway-based analysis approaches use different research designs,
which can be categorized into ORA (Over-representation analysis), FCS
(Functional class scoring) and pathway topology based methods. All of which
aim to find a subset of genes, e.g., significantly differentially
expressed genes, genes associated with a certain pathway more often than
expected given the total set of examined genes, e.g.~the whole genome
background.  ORA \cite{} is the first and the most basic method of pathway
analysis. It uses a DEG list with user defined cut-off for the log-fold
change and \textit{p}-value (most commonly using absolute log-fold change
$\geq$ 2 and \textit{p}-value $\leq$ 0.05). Subsequently, sets of genes
associated with annotated pathways are tested for being over-represented in
the set of DEGs. To this end, hyper-geometric distribution, chi-square
tests, binomial probability or the Fisher’s exact test are used. Thereby
the information of the topology of genes in the pathways is
neglected~\cite{Bayer}. Furthermore, ORA assumes that the biological
pathways are independent of each other and ignores the fact that they
cross-talk and overlap~\cite{Khatri2012,Campos}.

>>>>

Existing pathway-based analysis approaches use different research
designs, which can be categorized into ORA (Over-representation
analysis), FCS (Functional class scoring) and pathway topology based
methods. All of which aim to find a subset of genes, e.g.,
significantly differentially expressed genes, genes associated with a
certain pathway more often than expected given the total set of
examined genes, e.g.~the whole genome background.  \ILH{ORA \cite{} is
  the first and the most basic method of pathway analysis.} It uses a
DEG list with user defined cut-off for the log-fold change and
\textit{p}-value (most commonly using absolute log-fold change $\geq$
2 and \textit{p}-value $\leq$ 0.05). Subsequently, sets of genes
associated with annotated pathways are tested for being
over-represented in the set of DEGs. To this end, hyper-geometric
distribution, chi-square tests, binomial probability or the Fisher’s
exact test are used. Thereby the information of the topology of genes
in the pathways is neglected~\cite{Bayer}. Furthermore, ORA assumes
that the biological pathways are independent of each other and ignores
the fact that they cross-talk and overlap~\cite{Khatri2012,Campos}.
